Multi-line Intensity Mapping

### 2019-04-14 paper/ms.tex
Add thoughts section
Update ms.tex
Minor kmax changes

We are concerned with the problem of estimating the power spectrum of each
line only from the three cross-spectra. To be more concrete, we model each
auto-spectrum and cross-spectrum as,
\beq\label{eq:auto_xps}
\begin{split}
\ps{i}(k,z) &= B_i(z)^2 \denps(k,z) \\
\xps{i}{j}(k,z) &= B_i(z) B_j(z) \denps(k,z)\text{,}
\end{split}
\eeq
where $B_i(z) \equiv b_i(z) \avg{I_i}(z)$. We will generally suppress the
redshift and $k$ arguments for brevity. We can model the auto-spectra and
cross-spectra in this way only on sufficiently large scales, i.e. only when
$k<\kmax$ for some value of $k_{\text{max}}$. The value of \kmax{} is set by
two conditions. First, we must have that linear biasing is a good description
for each field $i$. This way $B_i$ for each line will be independent of $k$.
Second, for each pair of lines $(i,j)$ we must have that $\abs{r_{i,j}(k)} =
1$ when $k<\kmax$.

@@

\subsection{\CO{} Forecasts for CCAT-p and CONCERTO} \label{ssec:forecasts_tf}
Armed with some intuition from the simple white noise-dominated case, we now
turn to forecasting constraints that can be placed on the CO bias factors. Our
modelling of the \CO{} intensity as a function of redshift follows
\citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
assume that $b_i=3$ for each CO line.

>>>>

We are concerned with the problem of estimating the power spectrum of each
line only from the three cross-spectra. To be more concrete, we model each
auto-spectrum and cross-spectrum as,
\beq\label{eq:auto_xps}
\begin{split}
\ps{i}(k,z) &= B_i(z)^2 \denps(k,z) \\
\xps{i}{j}(k,z) &= B_i(z) B_j(z) \denps(k,z)\text{,}
\end{split}
\eeq
where $B_i(z) \equiv b_i(z) \avg{I_i}(z)$. We will generally suppress the
redshift and $k$ arguments for brevity. We can model the auto-spectra and
cross-spectra in this way only on sufficiently large scales, i.e. only when
$k<\kmax$ for some value of \kmax{}. The value of \kmax{} is set by two
conditions. First, we must have that linear biasing is a good description for
each field $i$ so that $B_i$ for each line is independent of $k$. Second, for
each pair of lines $(i,j)$ we must have that $\abs{r_{i,j}(k)} = 1$ when
$k<\kmax$.

@@

\subsection{\CO{} Forecasts for CCAT-p and CONCERTO} \label{ssec:forecasts_tf}
Armed with some intuition from the simple white noise-dominated case, we now
turn to forecasting constraints that can be placed on the CO bias factors. Our
modelling of the \CO{} intensity as a function of redshift follows
\citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
assume that $b_i=3$ for each \CO{} line.

\section{Thoughts}
Like doing a matched filter??? Trying to understand intuitively why this
works. If you have a super well measured field, then its like you're God who
knows that the density field is. Its almost like using that density field as a
matched filter?
